% $Id$

\documentclass[a4paper, 10pt] {article}

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\usepackage{sansmathfonts}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{multicol}

\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

\setlength{\parindent}{0mm}
\fontsize{10}{18}

\pagenumbering{gobble} % Disable page numbers

\pdfinfo{
/Title (Conall O'Brien Curriculum Vitae)
/Author (Conall O'Brien)
}

\begin{document}

\begingroup
  \centering
  \LARGE \textbf{Conall O'Brien}\\[1.5em]
\endgroup

% section*{Contact Details}

\begingroup
  \centering
  \small
      conall@conall.net \\
      +353 (0)87 9194139 \\
      Dublin, Ireland $\cdot$ Hybrid/Remote \\
      https://www.conall.net \\
      https://www.linkedin.com/in/conall \\
      \vspace{5mm} %5mm vertical space
  \normalsize
\endgroup

\begingroup
  \centering
  \large \textbf{Staff Site Reliability Engineer}\\[1em]
\endgroup

\section*{About}

Accomplished Staff Site Reliability Engineer with extensive experience in
large-scale infrastructure, AI/GPU cloud environments, observability,
SRE best practices, and technical leadership. Led design, implementation,
and monitoring of multiple large-scale systems, establishing best practices
across multiple organisations. Developed, mentored, and provided technical
direction to multiple teams focused on excellence and execution. Served as
the founding engineer for multiple SRE teams, including Google Network
Infrastructure SRE, Google Capacity Delivery SRE, and Crusoe AI Dublin SRE.
Has operated across global technical organisations in diverse, fast-changing,
and complex environments. Served as Senior Incident Commander and accredited
Kepner-Tregoe Practitioner. Excellent interpersonal communication and
organisational skills with an ability to navigate ambiguity, simplify, and
refine solutions. Out-of-the-box problem solver with a continuous evolution
mindset. Key strengths: leadership, integrity, collaborative, curious,
critical thinking, solution focused, detail orientated, analytical, self
starter, and strong team player.

\section*{Skills}

\begin{itemize}[noitemsep]
\item SRE/DevOps
  \begin{itemize}[noitemsep]
  \item Designing, Monitoring, Debugging \& Re-Architecture of Large Scale Systems
  \item Process Engineering, Workflow Definition/Optimisation, Automation Systems
  \item Continuous Integration/Continuous Delivery of Configuration \& Binary changes
  \item Incident Management (including User Facing \& Media Covered Events), Blameless Postmortems
  \item SRE Best Practices, Disaster Preparedness, User Interface (UI) \& User Experience (UX)
  \item Capacity Planning, Training, Technical Documentation
  \item Policy Formation \& Definition of Best Practices
  \end{itemize}
\item Soft Skills
  \begin{itemize}[noitemsep]
  \item Technical Leadership, Project Planning, Navigating Ambiguity, Mentoring
  \item Cross Timezone Collaboration, Cross Team Collaboration, Time Management
  \item Agile Planning and Execution, SDLC Process
  \item Personal Organisation, Emotional Intelligence, Self Directed Learning
  \item Technical Interviewing
  \end{itemize}
\item Technologies:
  \begin{itemize}[noitemsep]
  \item Operating Systems/Environments: Linux (Debian, Ubuntu, Red Hat), FreeBSD, MacOS X / MacOS, JunOS, Apple iOS
  \item Cloud Technologies: Containers, Container Orchestration (Google's Borg, Kubernetes), Terraform/OpenTofu
  \item CI/CD: GitHub Actions, Azure DevOps Pipelines, Gitlab CI, ArgoCD, Ansible/AWX
  \item Source Control: Piper (Google's Internal Perforce derivative), Git, Mercurial, Subversion, Perforce, CVS, RCS
  \item AI Tooling: Claude, Claude Code, Gemini, Windsurf, ChatGPT, Custom MCPs
  \item Programming Languages: Go, Python (including Django Framework), Bash
  \item Query Languages: PromQL, BigQuery, SQL, JQL, KQL
  \item Markup Languages \& Documentation: HTML, Markdown, GraphViz DOT, D2, \LaTeX, Wiki
  \end{itemize}
\end{itemize}  

\newpage

\section*{Employment History}

\subsection*{Crusoe AI}

\subsubsection*{Senior II Site Reliability Engineer (September 2024 - Current)}

Crusoe.ai is a sustainable energy focused "neocloud" Cloud computing provider, operating in the AI infrastructure space. They provide bare-metal,
VM and managed GPU-as-a-service solutions for LLM training and LLM Inference, powered by NVIDIA (H100, H200, B200, GB200, etc)
and AMD (MI355X, etc) GPUs.

I was the first engineer and third employee hired outside of the US. Worked with local manager \& recruiter to help grow the local SRE team to 15
\& the local office to 35+.

\begin{itemize}[noitemsep]
	\item Overhauled SRE onboarding, replacing tribal knowledge with structured documentation, recorded talks \& a peer-forum, measurably reducing ramp time for
	      every subsequent SRE hire
	\item Designed \& implemented a managed, CI/CD driven, multi-environment synthetic observability platform (Cloudprober) spanning VM control plane, CrusoeCloud,
	      Kubernetes \& bare-metal fleet; onboarded 8+ internal teams as users. Contributed upstream fixes to open-source Cloudprober
	\item Became the observability \& PromQL/MetricQL expert across SRE, Engineering \& Customer Success
	\item Served as Incident Commander for 20+ SEV1/SEV2 incidents over 4 months, authoring postmortems and driving systemic fixes; became accredited Kepner-Tregoe Practitioner
	\item Joined SDN oncall embedded rotation; identified \& fixed underlying root causes for repeating oncall issues, landed 5x - 10x scaling of the SDN control plane
	      through load balancer tuning, horizontal pod autoscaling \& targeted Kubernetes optimisations
    \item Closed multiple automation engine observability gaps by publishing both Ansible/AWX playbook execution history \& fleet-wide node metadata as queryable
	      metrics; resulting impacts included reducing detection time of automation-executed changes during incidents from O(hours) to O(minutes), \& a
		  90+\% reduction in non-actionable pages
\end{itemize}

\subsection*{DocuSign}

\subsubsection*{Lead Site Reliability Engineer (September 2023 - March 2024)}

Joined the fledgling TechOps SRE Organisation responsible for the reliability of DocuSign products and infrastructure,
as their first member outside of the US.

\begin{itemize}[noitemsep]
	\item Onboarded for services running in both AWS and Azure cloud environments
 	\item Joined the Senior Incident Commander oncall rotation
 	\item Advocated SRE and Engineering Best Practices across multiple business units by leading by example
\end{itemize}

\subsection*{Google}

\subsubsection*{Senior Site Reliability Engineer - Capacity Delivery (June 2021 - July 2023)}

The Turnup Organisation, responsible for the timely delivery \&
decommissioning of Google's compute resources. I was the first member
outside the US.

\begin{itemize}[noitemsep]
	\item Built and developed teams and provided bootstrapping, training, 
		on-boarding \& mentoring. Grew 7+ external hires into a high performing \&
		productive, local team.
  	\item Navigated ambiguity surrounding new hybrid datacenter building design.
		Collaborated with Security, Legal, Procurement, Deployment \& 
		Engineering to document specifics, to preempt miscommunication across groups.
	\item Identified \& drove preemptive changes to processes, tooling \& simplifying systems
		architecture \& was Tech Lead of a geographically diverse team.
	\item Simplified \& modernised resource management tooling across cross functional teams.
	\item Led OKR planning, consultations, navigating ambiguity \& cross team collaboration. Member
		of the team leadership group.
\end{itemize}

\newpage % Start a new page, so we don't cut a subsection in two

\subsubsection*{Senior Site Reliability Engineer - Network Infrastructure (April 2016 - June 2021)}

Member of the Network Infrastructure team, responsible for running
Google's network. This team was formed following the reorganisation of
~100 Network Engineers into the SRE Organisation.

\begin{itemize}[noitemsep]
	\item Specialised in unified monitoring solutions and acted as observability expert across multiple teams.
	\item Taught and mentored SRE Practices, Large Scale Systems Design, Monitoring \& Practical Scripting to multiple teams.
 	\item Hosted two interns, one of which successfully converted to a full-time Site Reliability Engineer
	\item Documented \& published Google SRE wide best practices for alerting.
	\item Awarded a 2021 Feat of Engineering Award, for SRE Lead of a cross functional team which decommissioned a 15+ year old blackbox
		monitoring tool. Replaced packet drop alerting with new SLO targets \& Error Budget concepts.
	\item Served as an Incident Responder to numerous user facing outages of various severity, including some with real-time media coverage
\end{itemize}

\subsubsection*{Senior Site Reliability Engineer - Search (January 2013 - March 2016)}

Member of the Search SRE team, responsible for Google Websearch.

\begin{itemize}[noitemsep]
	\item Led team of experts in the observability of Websearch providing guidance \& continuous improvements.
	\item Developed multiple features and member of Core Viceroy team, a Google internal equivalent of Managed Grafana.
  	\item Led an effort to create a single touch, automated CI/CD release pipeline for the Static HTTP Server powering Google Websearch \& YouTube.
   	\item Hosted an intern, who successfully converted to a full-time Site Reliability Engineer
	\item Achieved sub-linear growth through Problem Solving \& Toil Reduction, Process Engineering \& Automation Development.
	\item Responded to Incident Management of user facing outages, occasionally critical issues with media coverage.
 	\item Drove hardware upgrades \& rolled out IPv6 connectivity to globally distributed, out-of-band disaster recovery access systems.
\end{itemize}

\subsubsection*{Site Reliability Engineer - Traffic (June 2009 - December 2012)}

Member of the Traffic SRE team, responsible for ingress \& egress load
balancing for all Google products and the Google CDN. 

\begin{itemize}[noitemsep]
  \item Qualified \& rolled out 2nd generation IPv6 Load Balancing, enabling World IPv6 Day \& World IPv6 Launch.
	\item Acted as Observability expert for software control systems, load balancers, \& CDN components.
	\item Planned Capacity of software stacks, load balancers, \& CDN components.
 	\item Led a small group responsible for egress load balancing service.
  	\item Formed a group to maintain globally distributed, out-of-band disaster recovery access systems. Developed monitoring and alerting to
   		detect issues across the OOB systems.
 	\item Hosted an intern, who successfully converted to a full-time Product Manager
	\item Designed \& implemented a Cluster Health Console; a cross-cutting RAG status dashboard spanning all Google infrastructure
	    within a cluster, used by Incident Commanders to debug low-level issues \& inform decisions such as whether to perform an Emergency Power-Off
\end{itemize}

\subsubsection*{Systems Engineer - SysOps (June 2006 - June 2009)}

Member of the SysOps team, responsible for all systems infrastructure on
the corporate network.

\begin{itemize}[noitemsep]
	\item Designed \& implemented a multi O/S system deployment tracker
	\item Owned multiple corporate IT services
	\item Identified \& executed numerous projects with a focus on toil reduction
\end{itemize}

\newpage % Start a new page, so we don't cut a subsection in two

\subsection*{Earlier Career}

\subsubsection*{Systems \& Network Administrator - School of Mathematics, University of Dublin, Trinity College}

\section*{Professional Certifications}

\begin{itemize}[noitemsep]
  \item PagerDuty Incident Management
  \item Kepner-Tregoe: Practitioner in Troubleshooting
\end{itemize}

\section*{Volunteering}

\begin{itemize}[noitemsep]
  \item Technical Contributor: Prometheus.io, Cloudprober
  \item Technical Mentor: CoderDojo Bray
  \item Port Maintainer: FreeBSD, MacPorts
\end{itemize}

\section*{Education}

\begin{itemize}
  \item BA(Mod) Hons in Computer Science - University of Dublin, Trinity College
\end{itemize}

\section*{Interests}

Computers, Open Source Software, Home Automation, Electronics, Fitness, Travel, Photography, Woodwork,
Home-brewing Beer, Cooking, 3D-Printing, Laser Cutting

\end{document}
